### 2024-02-12 paper/paper.qmd
first draft of an explaination of figure1

---
title: "The Unintended Consequences of Energy Reduction"
subtitle: "How an Act of Environmental Protection Led to the Deaths of Many"
author:
  - Alex Pang
  - Irene Hyunh
  - Tara Chakkithara
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
pdf-engine: pdflatex
format:
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
include: false
warning: false
message: false
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

![Figure 1](../other/figures/figure1.png)

The 2011 Fukushima disaster changed the relationship Japanese citizens had with nuclear energy. From the 160, 000 Fukushima residents that had to evacuate the city to the citizens who may not have been affected directly, the public as a whole turned their backs against  the entire industry [science direct].

Before the accident, nuclear energy made up 25% of Japan’s energy market. After the accident, the market share stayed under 1.7% until 2016. The Democratic Party of Japan itself took initiative and implemented a new energy policy to “phase out nuclear power,” [intchopen] despite formerly having close ties to the industry in attempts to reduce CO2 pollution. [enpolicy one year later]

Fossil fuels grew to dominate Japan’s energy market as many reactors were shut down. In 2011 itself, oil usage rose by around 85% while natural gas increased by 25%. [enpolicy one year later]

This change had a huge impact on the price and consumption of electricity. Relative to the mean price of electricity in 2011, by 2013 the price of electricity had increased to over 10% and almost reached an increase of 20% by 2014. Concurrently, electricity consumption itself kept decreasing year after year as it became less affordable. [figure 1]

A good reason for this market shift is that most of the fossil fuels that Japan utilizes are exported from other countries, which makes them expensive. [enpolicy one year later] The lack of nuclear power also reduced more affordable options for consumers.

The trend of increasing electricity prices and decreasing electricity consumption may persist into the future. The current government of Japan reversed the nuclear energy policy, but low public demand for nuclear energy still persists. Thus the prices will stay high as people continue to consume fossil fuels. There are also barriers to nuclear power that help to persist this trend. One barrier is the Nuclear Regulation Authority which created tougher safety regulations for reactors. Another are injunctions that citizens can bring forth to prevent the operation of nuclear reactors. After the Fukushima tragedy many courts in Japan may grant these injunctions for safety reasons.  [intchopen]

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-02-14 paper/paper.qmd
weaknesses and next steps added, pls review

@@
 author:
-  - Alex Pang
+  - Yi Fei Pang
   - Irene Hyunh
@@
 
-Weaknesses and next steps should also be included.
+A few weaknesses with the analysis comes from the limitation of data.The scope of analysis for the post-Fukushima incident and the effects of the energy policy is only Japan.
+There is no comparison to other countries and their markets trends after nuclear accidents such as Ukraine with the Chernobyl incident.
+Furthermore, the data is limited only from the Fukushima incident up until 2016 allowing for a short term analysis.
+The physical effects of nuclear incidents along with the economic effects of the energy policy are both issues that can use a more long term approach.
+Additionally, there is a lack of robustness as the analysis is fixated on the effects caused by the transition from nuclear energy to fossil fuels.
+However, there are other energy sources such as renewable energy which includes solar and wind energy that should be taken into consideration.
+
+The next steps would be to find more recent data.
+As aforementioned, the datasets only extend until 2016 and to complete a long-term analysis, more recent Japanese energy data needs to be collected.
+Moreover, data from before and after other global nuclear incidents should be gathered and evalauted in comparison to Fukushima to evaluate whether the Japanese government's apporoach was the most optimal.
+Another step that can be taken to futher the analysis could be to explore more granular effects.
+For example, in addition to looking at how temperatures and strokes can be correlated (pls verify we did this?), other factors such as energy price variation and seasons or energy jobs and employment rates can be observed as well.
 

### 2024-02-14 scripts/generate_figures/generate_figure2.R
generated a figure on the percent of nuclear energy produced domestically

@@ -1,0 +1,17 @@
+library(tidyverse)
+
+data <- read_csv("data/analysis_data/clean_domestic.csv")
+
+plot <- data |>
+  ggplot(
+    aes(x = year)
+  ) +
+  theme_fivethirtyeight() +
+  theme_bw() +
+  scale_x_continuous(breaks = data$year) +
+  geom_point(aes(y = percent_nuclear)) +
+  geom_path(aes(y = percent_nuclear)) +
+  labs(x = "Year", y = "Percent of Nuclear Energy Produced") +
+  ggtitle("Percent of Nuclear Energy Produced Domestically")
+
+ggsave("other/figures/figure2.png", plot)

### 2024-02-14 paper/paper.qmd
Added abstract and removed unecessary code

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Nuclear energy is a clean power source that produces electricity while operating with low-carbon emissions.
+Although nuclear power generation has its advantages, many concerns have been raised regarding its safety after the Fukushima nuclear accident of 2011.
+This paper analyzes the utilization of nuclear energy, the price of electricity and electricity consumption, and the temperature-mortality relationship in Japan before and after the accident.
+We reveal that the use of nuclear energy in Japan sharply decreased following the nuclear accident, resulting in a power shortage and surge in electricity prices across Japan.
+This prompted the country’s government to push an energy saving mindset to the public, and as a result, electricity consumption plummeted.
+However, we find that the government’s efforts created adverse effects as days with high temperatures coupled with an energy saving mindset led to a higher mortality rate.
+These findings prompt discussions about the true cost of energy saving."
 pdf-engine: pdflatex
@@
 library(tidyverse)
-library(palmerpenguins)
 ```
@@
 
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
 Talk more about it.
@@
 (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
 
@@
 Our results are summarized in @tbl-modelresults.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
 
@@
 
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
 ## Diagnostics
@@
 
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
 \newpage

### 2024-02-14 paper/paper.qmd
Added abstract and removed unecessary code
added to next steps/included intro figure5

@@
 
+![Figure 5](../other/figures/figure5.png)
+After the Fukushima incident, the government tried to ensure sufficient backup capacity to avoid power blackouts.
+While other factors could affect the saving target, the primary determinant of the saving target was a region’s dependence on nuclear power before the accident.(Kim, et al.) This caused more health issues for individuals as they were encouraged to not use AC and other cooling devices during hotter days.
+Previous to the implementation of the energy policy, throughout the period between 1960 and 2004, the mortality rate at over 32.2 degrees Celsius has dropped tremendously while that of between 26.7-32.3 degrees Celsius remained consistent.
+However, it becomes evident that after the policy implementation, at similar ranges of 25-30 degrees Celsius and over 30 degrees Celsius produced a higher mortality rate.
+[figure 5]
+
 You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
@@
 Another step that can be taken to futher the analysis could be to explore more granular effects.
-For example, in addition to looking at how temperatures and strokes can be correlated (pls verify we did this?), other factors such as energy price variation and seasons or energy jobs and employment rates can be observed as well.
+For example, in addition to looking at how ambulance calls and heat strokes can be correlated and how increased temperature can cause higher mortality rates before and after the energy policy, other factors such as energy price variation and seasons or energy jobs and employment rates can be observed as well.
 

### 2024-02-14 paper/paper.tex
added to next steps/included intro figure5

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=30mm,left=20mm,heightrounded]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{siunitx}

  \newcolumntype{d}{S[
    input-open-uncertainty=,
    input-close-uncertainty=,
    parse-numbers = false,
    table-align-text-pre=false,
    table-align-text-post=false
  ]}

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The Unintended Consequences of Energy Reduction},
  pdfauthor={Yi Fei Pang; Irene Hyunh; Tara Chakkithara},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{The Unintended Consequences of Energy Reduction\thanks{Code and
data are available at: LINK.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{How an Act of Environmental Protection Led to the Deaths of
Many}
\author{Yi Fei Pang \and Irene Hyunh \and Tara Chakkithara}
\date{February 13, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\begin{figure}

{\centering \includegraphics{../other/figures/figure1.png}

}

\caption{Figure 1}

\end{figure}

The 2011 Fukushima disaster changed the relationship Japanese citizens
had with nuclear energy. From the 160, 000 Fukushima residents that had
to evacuate the city to the citizens who may not have been affected
directly, the public as a whole turned their backs against the entire
industry {[}science direct{]}.

Before the accident, nuclear energy made up 25\% of Japan's energy
market. After the accident, the market share stayed under 1.7\% until
2016. The Democratic Party of Japan itself took initiative and
implemented a new energy policy to ``phase out nuclear power,''
{[}intchopen{]} despite formerly having close ties to the industry in
attempts to reduce CO2 pollution. {[}enpolicy one year later{]}

Fossil fuels grew to dominate Japan's energy market as many reactors
were shut down. In 2011 itself, oil usage rose by around 85\% while
natural gas increased by 25\%. {[}enpolicy one year later{]}

This change had a huge impact on the price and consumption of
electricity. Relative to the mean price of electricity in 2011, by 2013
the price of electricity had increased to over 10\% and almost reached
an increase of 20\% by 2014. Concurrently, electricity consumption
itself kept decreasing year after year as it became less affordable.
{[}figure 1{]}

A good reason for this market shift is that most of the fossil fuels
that Japan utilizes are exported from other countries, which makes them
expensive. {[}enpolicy one year later{]} The lack of nuclear power also
reduced more affordable options for consumers.

The trend of increasing electricity prices and decreasing electricity
consumption may persist into the future. The current government of Japan
reversed the nuclear energy policy, but low public demand for nuclear
energy still persists. Thus the prices will stay high as people continue
to consume fossil fuels. There are also barriers to nuclear power that
help to persist this trend. One barrier is the Nuclear Regulation
Authority which created tougher safety regulations for reactors. Another
are injunctions that citizens can bring forth to prevent the operation
of nuclear reactors. After the Fukushima tragedy many courts in Japan
may grant these injunctions for safety reasons. {[}intchopen{]}

You can and should cross-reference sections and sub-sections. We use R
Core Team (2023) and Wickham et al. (2019).

The remainder of this paper is structured as follows.
Section~\ref{sec-data}\ldots.

\hypertarget{sec-data}{%
\section{Data}\label{sec-data}}

Some of our data is of penguins (\textbf{?@fig-bills}), from Horst,
Hill, and Gorman (2020).

Talk more about it.

And also planes (\textbf{?@fig-planes}). (You can change the height and
width, but don't worry about doing that until you have finished every
other aspect of the paper - Quarto will try to make it look nice and the
defaults usually work well once you have enough text.)

Talk way more about it.

\hypertarget{model}{%
\section{Model}\label{model}}

The goal of our modelling strategy is twofold. Firstly,\ldots{}

Here we briefly describe the Bayesian analysis model used to
investigate\ldots{} Background details and diagnostics are included in
Appendix~\ref{sec-model-details}.

\hypertarget{results}{%
\section{Results}\label{results}}

Our results are summarized in \textbf{?@tbl-modelresults}.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{sec-first-point}{%
\subsection{First discussion point}\label{sec-first-point}}

\hypertarget{second-discussion-point}{%
\subsection{Second discussion point}\label{second-discussion-point}}

\hypertarget{third-discussion-point}{%
\subsection{Third discussion point}\label{third-discussion-point}}

\hypertarget{weaknesses-and-next-steps}{%
\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}}

A few weaknesses with the analysis comes from the limitation of data.The
scope of analysis for the post-Fukushima incident and the effects of the
energy policy is only Japan. There is no comparison to other countries
and their markets trends after nuclear accidents such as Ukraine with
the Chernobyl incident. Furthermore, the data is limited only from the
Fukushima incident up until 2016 allowing for a short term analysis. The
physical effects of nuclear incidents along with the economic effects of
the energy policy are both issues that can use a more long term
approach. Additionally, there is a lack of robustness as the analysis is
fixated on the effects caused by the transition from nuclear energy to
fossil fuels. However, there are other energy sources such as renewable
energy which includes solar and wind energy that should be taken into
consideration.

The next steps would be to find more recent data. As aforementioned, the
datasets only extend until 2016 and to complete a long-term analysis,
more recent Japanese energy data needs to be collected. Moreover, data
from before and after other global nuclear incidents should be gathered
and evalauted in comparison to Fukushima to evaluate whether the
Japanese government's apporoach was the most optimal. Another step that
can be taken to futher the analysis could be to explore more granular
effects. For example, in addition to looking at how temperatures and
strokes can be correlated (pls verify we did this?), other factors such
as energy price variation and seasons or energy jobs and employment
rates can be observed as well.

\newpage

\appendix

\hypertarget{appendix}{%
\section*{Appendix}\label{appendix}}
\addcontentsline{toc}{section}{Appendix}

\hypertarget{additional-data-details}{%
\section{Additional data details}\label{additional-data-details}}

\hypertarget{sec-model-details}{%
\section{Model details}\label{sec-model-details}}

\hypertarget{posterior-predictive-check}{%
\subsection{Posterior predictive
check}\label{posterior-predictive-check}}

In \textbf{?@fig-ppcheckandposteriorvsprior-1} we implement a posterior
predictive check. This shows\ldots{}

In \textbf{?@fig-ppcheckandposteriorvsprior-2} we compare the posterior
with the prior. This shows\ldots{}

\hypertarget{diagnostics}{%
\subsection{Diagnostics}\label{diagnostics}}

\textbf{?@fig-stanareyouokay-1} is a trace plot. It shows\ldots{} This
suggests\ldots{}

\textbf{?@fig-stanareyouokay-2} is a Rhat plot. It shows\ldots{} This
suggests\ldots{}

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-palmerpenguins}{}}%
Horst, Allison Marie, Alison Presmanes Hill, and Kristen B Gorman. 2020.
\emph{Palmerpenguins: Palmer Archipelago (Antarctica) Penguin Data}.
\url{https://doi.org/10.5281/zenodo.3960218}.

\leavevmode\vadjust pre{\hypertarget{ref-citeR}{}}%
R Core Team. 2023. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\leavevmode\vadjust pre{\hypertarget{ref-rohan}{}}%
Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.

\end{CSLReferences}

\end{document}

### 2024-02-14 paper/paper.qmd
Wrote introduction with citations and references

@@
 # Introduction
+The 2011 Fukushima nuclear disaster changed the relationship Japanese citizens have with nuclear energy.
+From the 160,000 Fukushima residents that had to evacuate the city to the citizens who may not have been affected directly, the public as a whole turned their backs against the entire nuclear industry [@scienceDirect].
+However, we find that Japan’s halt in nuclear energy generation is not without its fatal consequences.
+
+The nuclear disaster was triggered by an earthquake, generating tsunami waves that flooded the Fukushima Daiichi plant and shut off power to its cooling systems, causing the meltdown of three reactor cores and radiation release [@britannica].
+Fortunately, there was no death toll as a result of radiation exposure; however the aftermath of the accident did not leave the Japanese public unscathed.
+Thousands of residents’ mental and physical health deteriorated as they were forced to evacuate and be permanently relocated [@CDC].
+According to the CDC, the disaster triggered an increase in deaths among elderly citizens placed in temporary housing and a rise in post-traumatic stress disorder rates among those affected [@CDC].
+The public lost trust in nuclear energy and demanded the use of nuclear power plants be eradicated from Japan [@intechopen].
+
+As a response to the growing public outcry, the government of Japan took swift action to significantly reduce nuclear power generation by implementing a new energy policy to eliminate nuclear power by 2030 [@intechopen].
+Before the accident, nuclear energy comprised 25% of Japan’s energy market [@intechopen].
+After the accident, the market share stayed under 1.7% until 2016 [@intechopen].
+The significant and abrupt reduction in overall power generation caused Japan to steer towards potential countrywide power shortages [@guardian].
+To combat this, the government pushed a power saving campaign to the public [@guardian].
+In fear of blackouts, energy saving was quickly adopted by Japanese citizens, resulting in a considerable decrease in electricity consumption [@intechopen].
+
+The energy saving campaign was not the sole factor in the sharp decline in energy consumption as the price for electricity also surged.
+As many nuclear reactors were shut down, fossil fuels grew to dominate Japan’s energy market.
+In 2011, oil usage rose by an estimated 85% while natural gas increased by 25% [@energyPolicyYearLater].
+This shift to predominate fossil fuel usage had a substantial impact on the price and consumption of electricity as the majority of fossil fuels utilized in Japan are imported from other countries, resulting in expensive prices [@energyPolicyYearLater].
+Relative to the mean price of electricity in 2011, the price of electricity had increased by over 10% in 2013 and further increased by nearly 20% in 2014 [@energyPolicyYearLater].
+Consequently, electricity consumption decreased each year as the commodity became less affordable.
+The Japanese government was successful in reducing energy consumption; however, their energy-saving policies and campaigns cause potential detrimental consequences to the public.
+
+In this paper, we follow He and Tanaka’s paper to produce a reproduction of their findings and discuss further about Japan’s future as their government reverses their stance on nuclear energy and begins restarting the use of old power plants as a response to fossil fuel shortages and the public pressure to reduce the country’s carbon footprint.
+We analyze the major reduction in energy consumption from 2005 to 2015 caused by the decline in nuclear energy usage, the sharp increase in electricity prices and the energy saving campaign pushed by the Japanese government to investigate their impact on mortality rate in high temperatures.
+We find that the mortality rate increases as energy consumption decreases.
+An important finding is that air conditioner usage plays a vital role in preventing deaths related to high temperatures.
+Therefore, the pressure to conserve energy and hence not utilize air conditioners, increases the mortality rate in Japan.
+
+The remainder of this paper is structured as follows: the Data section details the collection
+and processing of nuclear energy production, energy consumption and energy price, and temperature-mortality data.
+Additionally, the section includes discussion on the measurement of the original dataset.
+The following Results section displays and analyzes tables
+and figures that illustrate the trends found in the data. The Discussion section draws conclusions from those tables and figures and details the importance of our findings and weaknesses of our paper.
 
 ![Figure 1](../other/figures/figure1.png)
-
-The 2011 Fukushima disaster changed the relationship Japanese citizens had with nuclear energy.
-From the 160, 000 Fukushima residents that had to evacuate the city to the citizens who may not have been affected directly, the public as a whole turned their backs against the entire industry [science direct].
-
-Before the accident, nuclear energy made up 25% of Japan’s energy market.
-After the accident, the market share stayed under 1.7% until 2016.
-The Democratic Party of Japan itself took initiative and implemented a new energy policy to “phase out nuclear power,” [intchopen] despite formerly having close ties to the industry in attempts to reduce CO2 pollution.
-[enpolicy one year later]
-
-Fossil fuels grew to dominate Japan’s energy market as many reactors were shut down. In 2011 itself, oil usage rose by around 85% while natural gas increased by 25%. [enpolicy one year later]
-
-This change had a huge impact on the price and consumption of electricity.
-Relative to the mean price of electricity in 2011, by 2013 the price of electricity had increased to over 10% and almost reached an increase of 20% by 2014.
-Concurrently, electricity consumption itself kept decreasing year after year as it became less affordable.
-[figure 1]
-
-A good reason for this market shift is that most of the fossil fuels that Japan utilizes are exported from other countries, which makes them expensive.
-[enpolicy one year later] The lack of nuclear power also reduced more affordable options for consumers.
-
-The trend of increasing electricity prices and decreasing electricity consumption may persist into the future.
-The current government of Japan reversed the nuclear energy policy, but low public demand for nuclear energy still persists.
-Thus the prices will stay high as people continue to consume fossil fuels.
-There are also barriers to nuclear power that help to persist this trend.
-One barrier is the Nuclear Regulation Authority which created tougher safety regulations for reactors.
-Another are injunctions that citizens can bring forth to prevent the operation of nuclear reactors.
-After the Fukushima tragedy many courts in Japan may grant these injunctions for safety reasons.
-[intchopen]
-
 ![Figure 5](../other/figures/figure5.png)

### 2024-02-14 data/raw_data/weather/csv/get.py
extracted temperature data from raw weather data with clean_temperature.R

@@ -1,0 +1,9 @@
+# import requests
+# url_city= "https://www.data.jma.go.jp/gmd/risk/obsdl/top/station"
+# payload = {   
+#     'pd': '11'
+# }
+# citylist = requests.post(url_city,data = payload)
+# print(citylist.text)
+
+import pandas as pd

### 2024-02-14 scripts/data_cleaning/clean_temperature.R

@@ -1,0 +1,40 @@
+library(tidyverse)
+library(readxl)
+
+clean_csv <- function(file) {
+  data <- read_csv(sprintf("data/raw_data/weather/csv/%s_201.csv", file), skip = 6)
+  data <- data |>
+    select(1, 2, 3, 4) |>
+    rename(
+      year = names(data)[1],
+      month = names(data)[2],
+      day = names(data)[3],
+      temperature = names(data)[4]
+    )|>
+    filter(year >= 2005)
+  
+  return(data)
+}
+
+station_data <- read_excel("data/raw_data/weather/station.xlsx")
+
+total_data <- data.frame()
+count <- 1
+
+for (id in station_data$station_id) {
+  data <- clean_csv(id)
+  data <- data |>
+    mutate(
+      id = station_data$pref_id[count]
+    )
+  total_data <- rbind(total_data, data)
+  count <- count + 1
+}
+
+total_data <- total_data |>
+  group_by(id, year, month, day) |>
+  summarise(temperature_avg = mean(temperature, na.rm = TRUE)) |>
+  ungroup()
+
+
+write_csv(total_data, "data/analysis_data/clean_temperature.csv")

### 2024-02-14 paper/paper.qmd

@@
 This paper analyzes the utilization of nuclear energy, the price of electricity and electricity consumption, and the temperature-mortality relationship in Japan before and after the accident.
-We reveal that the use of nuclear energy in Japan sharply decreased following the nuclear accident, resulting in a power shortage and surge in electricity prices across Japan.
+We reveal that the use of nuclear energy in Japan sharply decreased following the nuclear accident, resulting in a power shortage scare and surge in electricity prices across Japan.
 This prompted the country’s government to push an energy saving mindset to the public, and as a result, electricity consumption plummeted.
-However, we find that the government’s efforts created adverse effects as days with high temperatures coupled with an energy saving mindset led to a higher mortality rate.
+However, we find that the government’s efforts created adverse effects as days with high temperatures coupled with an energy saving mindset led to a higher mortality rate and a shift to fossil fuel dependent energy poses grave consequences to the environment.
 These findings prompt discussions about the true cost of energy saving."

### 2024-02-15 scripts/generate_figures/generate_figure4.R
created 2 additional figures using heatstroke data

@@ -1,0 +1,18 @@
+library(tidyverse)
+library(ggthemes)
+
+data <- read_csv("data/analysis_data/stroke.csv")
+
+data <- data |>
+  group_by(period) |>
+  summarise(num = sum(people_transported, na.rm = TRUE))
+
+plot <- data |>
+  ggplot(
+    mapping = aes(x = period, y = num)
+  ) +
+  geom_bar(stat = "identity", fill = "lavender") +
+  theme_test() +
+  labs(x = "Period", y = "Number of Heatstroke Incidents")
+
+ggsave("other/figures/figure4.png", plot)

### 2024-02-15 scripts/generate_figures/generate_figure5.R

@@ -1,0 +1,28 @@
+library(tidyverse)
+library(ggthemes)
+
+data <- read_csv("data/analysis_data/stroke.csv")
+
+data <- data |>
+  group_by(period, prefecture_code) |>
+  summarise(num = sum(people_transported, na.rm = TRUE)) |>
+  ungroup()
+
+data <- data |>
+  filter(prefecture_code %in% c(13, 26, 27, 47, 31))
+
+data$prefecture_code <- factor(data$prefecture_code)
+plot <- data |>
+  ggplot(
+    aes(x = period, y = num, color = prefecture_code, group = prefecture_code)
+  ) +
+  scale_color_manual(values = c("blue", "red", "black", "red4", "cadetblue"),
+                     labels = c("Tokyo", "Kyoto", "Osaka", "Tottori", "Okinawa")) +
+  geom_point() +
+  geom_line(key_glyph = "point") +
+  theme_bw() +
+  theme(panel.background = element_rect(fill = "white")) +
+  labs(x = "Period", y = "Heatstroke Incidents", color = "Prefecture")
+
+
+ggsave("other/figures/figure5.png", plot)

### 2024-02-15 paper/paper.qmd

@@
 Before the accident, nuclear energy comprised 25% of Japan’s energy market [@intechopen].
-After the accident, the market share stayed under 1.7% until 2016 [@intechopen].
-The significant and abrupt reduction in overall power generation caused Japan to steer towards potential countrywide power shortages [@guardian].
+After the accident, its market share stayed under 1.7% until 2016 [@intechopen].
+The significant and abrupt reduction in overall power generation caused Japan to steer dangerously close to potential countrywide power shortages [@guardian].
 To combat this, the government pushed a power saving campaign to the public [@guardian].
@@
 
-The energy saving campaign was not the sole factor in the sharp decline in energy consumption as the price for electricity also surged.
+We find that the energy saving campaign was not the sole factor in the sharp decline in energy consumption as the price of electricity also surged.
 As many nuclear reactors were shut down, fossil fuels grew to dominate Japan’s energy market.
 In 2011, oil usage rose by an estimated 85% while natural gas increased by 25% [@energyPolicyYearLater].
-This shift to predominate fossil fuel usage had a substantial impact on the price and consumption of electricity as the majority of fossil fuels utilized in Japan are imported from other countries, resulting in expensive prices [@energyPolicyYearLater].
-Relative to the mean price of electricity in 2011, the price of electricity had increased by over 10% in 2013 and further increased by nearly 20% in 2014 [@energyPolicyYearLater].
+This shift to predominately fossil fuel usage had a substantial impact on the price and consumption of electricity as the majority of fossil fuels utilized in Japan are imported from other countries, resulting in expensive prices [@energyPolicyYearLater].
+Relative to the mean price of electricity in 2011, the price of electricity increased by over 10% in 2013 and further increased by nearly 20% in 2014 [@energyPolicyYearLater].
 Consequently, electricity consumption decreased each year as the commodity became less affordable.
-The Japanese government was successful in reducing energy consumption; however, their energy-saving policies and campaigns cause potential detrimental consequences to the public.
+The Japanese government was successful in reducing energy consumption; however, their energy-saving policies and campaigns may cause potential detrimental consequences to the public.
 
-In this paper, we follow He and Tanaka’s paper to produce a reproduction of their findings and discuss further about Japan’s future as their government reverses their stance on nuclear energy and begins restarting the use of old power plants as a response to fossil fuel shortages and the public pressure to reduce the country’s carbon footprint.
-We analyze the major reduction in energy consumption from 2005 to 2015 caused by the decline in nuclear energy usage, the sharp increase in electricity prices and the energy saving campaign pushed by the Japanese government to investigate their impact on mortality rate in high temperatures.
+In this paper, we follow He and Tanaka’s paper (2019) to produce a reproduction of their findings and discuss further about Japan’s future as their government reverses their stance on nuclear energy and begins restarting the use of old power plants as a response to fossil fuel shortages and the public pressure to reduce the country’s carbon footprint.
+We analyze the major reduction in energy consumption from 2005 to 2015 caused by the decline in nuclear energy usage, the sharp increase in electricity prices, and the energy saving campaign pushed by the Japanese government in order to investigate their impact on the mortality rate related to high temperatures.
 We find that the mortality rate increases as energy consumption decreases.
@@
 The remainder of this paper is structured as follows: the Data section details the collection
-and processing of nuclear energy production, energy consumption and energy price, and temperature-mortality data.
+and processing of nuclear energy production, energy consumption, energy price, and temperature-mortality data.
 Additionally, the section includes discussion on the measurement of the original dataset.
@@
 
-## First discussion point {#sec-first-point}
+Our findings give insight into the consequences of energy saving in Japan, particularly the potential fatalities that may occur.
+It is also important to discuss the growing use of fossil fuel dependent energy generation as a response to the Fukushima nuclear accident and its devastation on the environment.
 
-## Second discussion point
+## Findings
 
-## Third discussion point
+After the Fukushima accident, the Japanese public’s trust of nuclear power was retracted and the use of nuclear power began to diminish.
+Figure 1 emphasizes this sharp decline in nuclear power energy production in Japan.
+As a consequence of the decline in nuclear energy production, Figure 2 shows the extreme increase in energy prices and the decline in energy consumption.
+These findings can be attributed to the Japanese government urging the public to use less energy and the expensive cost of fossil fuel use for energy production.
+Figure 3 demonstrates that the energy saving campaign orchestrated by the government and the use of expensive fossil fuels can have harmful effects.
+Specifically, Figure 3 illustrates the potential increase in the mortality rate of Japanese citizens due to their reduction in energy consumption.
+In particular, Barreca et al.
+(2016) states that air condition usage reduces the mortality rate related to high temperatures by a significant amount [@barreca].
+By utilizing their findings and He and Tanaka’s (2019) findings, we draw the conclusion that the mortality rate increases by 0.8% during temperatures between 25°C and 30°C and by 0.19% during temperatures over 30°C [@heTanaka].
+This is significant as it demonstrates that the push for energy saving may cause fatalities in high temperature environments.
+This consequence of energy saving can be further illustrated by Figure 4 and Figure 5, whereby the number of heatstroke incidents sharply increased from 2010 to 2011.
+
+## Japan’s Relationship with Nuclear Energy and its Impact on the Public
+
+As shown in Figure 1, the use of nuclear energy is slowly becoming obsolete in Japan in light of the Fukushima accident.
+However, in 2022, the Japanese government announced a plan to revitalize the use of nuclear energy [@npr].
+This decision comes as a potential solution to fossil fuel shortages and the push for low carbon emissions.
+Nuclear energy production produces little waste, is less expensive to operate, and generates low carbon emissions [@energy].
+The government plans on maximizing the output of all existing nuclear power plants and they aim to build new reactors, proclaiming that nuclear energy will contribute to 20-22% of the country’s energy output by 2030 [@npr].
+The government reversed the nuclear energy policy, but low public demand for nuclear energy persists.
+Thus, energy prices will remain high as individuals continue to advocate against nuclear energy usage and turn to fossil fuels.
+Additionally, there are barriers to reinstating nuclear power generation that exacerbate the trend found in Figure 3.
+One barrier is the Nuclear Regulation Authority which enforced stricter safety regulations for reactors [@intechopen].
+Restarts of existing nuclear reactors have been slow due to these stricter regulations put in place following the Fukushima accident [@npr].
+Additionally, the government’s new stance on nuclear energy does not come without opposition by the public.
+One survivor of the Fukushima disaster voices their frustration, “The Fukushima disaster is not over yet and the government seems to have already forgotten what happened.” [@npr].
+Furthermore, citizens can bring forth injunctions to prevent the operation of nuclear reactors.
+After the Fukushima tragedy, many courts in Japan may grant these injunctions to protect the public's safety [@intechopen].
+Thus, as the return to nuclear energy is met with resistance, the use of fossil fuels persists; thereby causing the price of energy to increase and the consumption of energy to decrease, leading to potentially more fatalities in high temperatures.
+
+## Future Research Proceedings
+
+For future research, more data should be collected regarding deaths due to high temperatures to investigate its relationship with energy prices.
+Additionally, as global temperatures continue to soar each year, it is imperative that more environmentally friendly solutions to energy generation be adopted.
 

### 2024-02-15 scripts/simulate_data/simulate_data_energy.R
Finished simulation for figure 1 and 2

@@ -1,0 +1,77 @@
+#### Preamble ####
+# Purpose: Simulates energy prices and consumption in Japan from 2005 to 2015.
+# Date: 14 February 2024
+# License: MIT
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Simulate data ####
+set.seed(123) # For reproducibility 
+
+n <- 11 # Number of years in the figure from 2005 to 2015
+
+years_price <- rep(NA, times=n)
+years_consumption <- rep(NA, times=n)
+
+# Percent of energy price from 2005 to 2007
+# Should be 0.9-1%
+for (i in 1:3) {
+  years_price[i] <- (sample(9:10, 1))/10
+}
+
+# Percent of energy price in 2008
+# Should be 1-1.05%
+years_price[4] <-(sample(100:105, 1))/100
+
+# Percent of energy price from 2009 to 2010
+# Should be 0.9-1%
+for (i in 5:6) {
+  years_price[i] <- (sample(9:10, 1))/10
+}
+
+# Percent of energy price from 2011 to 2015
+# Should be increasing from around 1% to under 1.2%
+increase <- 0
+for (i in 7:n) {
+  years_price[i] <- 1 + increase
+  increase = increase + 0.05
+}
+
+# Percent of energy consumption from 2005 to 2008
+# Should be increasing from around 1% to under 1.1%
+increase <- 0
+for (i in 1:4) {
+  years_consumption[i] <- 1 + increase
+  increase = increase + 0.03
+}
+
+# Percent of energy consumption in 2009
+# Should be 0.7-1%
+years_consumption[5] <- (sample(7:10, 1))/10
+
+# Percent of energy consumption from 2010 to 2015
+# Should be decreasing from around 1.05% to close to 0%
+decrease <- 0
+for (i in 6:n) {
+  years_consumption[i] <- 1.05 - decrease
+  decrease = decrease + 0.05
+}
+
+simulated_data <-
+  tibble(
+    year = 2005:2015,
+    price = years_price,
+    consumption = years_consumption
+  )
+
+ggplot(simulated_data, aes(x=year)) +
+  geom_line(aes(y = years_price), color="blue") +
+  geom_line(aes(y = years_consumption), color="red") +
+  geom_point(aes(y = years_price), color="blue") +
+  geom_point(aes(y = years_consumption), color="red") +
+  theme_fivethirtyeight() +
+  theme_bw() +
[…]

### 2024-02-15 scripts/simulate_data/simulate_data_nuclear.R

@@ -15,17 +15,17 @@ n <- 11 # Number of years in the figure from 2005 to 2015
 years_nuclear <- rep(NA, times=n)
 
 # Percent of nuclear energy production from 2005 to 2010
-# Should be 20-30%
+# Should be 20-30% for all years
 for (i in 1:6) {
   years_nuclear[i] <- (sample(20:30, 1))
 }
 
 # Percent of nuclear energy production in 2011
-# Should be 5-10%
+# Should be 5-10% for all years
 years_nuclear[7] <- (sample(5:10, 1))
 
 # Percent of nuclear energy production from 2012 to 2015
-# Should be 0-5%
+# Should be 0-5% for all years
 for (i in 8:n) {
   years_nuclear[i] <- (sample(0:5, 1))
 }

### 2024-02-15 scripts/simulate_data/simulate_data_heatstroke.R
simulation of heatstroke data/tests for simulation completed

@@ -1,0 +1,40 @@
+#### Simulation for Heatstroke Analysis ####
+
+# The years for the data will be between 2008 and 2015
+years <- 2008:2015
+
+# The heatstroke cases will be randomly generated. However, there should be a
+# difference between the years before and after the energy policy theoretically
+heatstroke_cases <- numeric(length(years))
+for (i in 1:length(years)) {
+  if (years[i] < 2011) {
+    heatstroke_cases[i] <- sample(3000:6000, 1)
+  } else if (years[i] < 2013) {
+    heatstroke_cases[i] <- sample(5000:10000, 1)
+  } else {
+    heatstroke_cases[i] <- sample(3000:6000, 1)
+  }
+}
+
+# combine the years and heatstroke cases into a single dataframe
+data <- data.frame(Years = years, Heatstroke_Cases = heatstroke_cases)
+
+# Plotting
+barplot(data$Heatstroke_Cases, names.arg = data$Years, xlab = "Years", ylab = "Heatstroke Cases", main = "Heatstroke Cases per Year")
+
+#### Tests for Heatstroke Simulation ####
+
+# test if the years in the data set are from the appropriate years
+test1 <- all(data$Years == 2008:2015)
+
+# test to see if all heatstroke cases are within the given range
+test2 <- all(data$Heatstroke_Cases >= 3000 & data$Heatstroke_Cases <= 10000)
+
+# test that the length of the years and heatstroke cases are the same
+test3 <- length(data$Years) == length(data$Heatstroke_Cases)
+
+# If any of the 3 tests fail or return false, there is an issue with the data.
+test1
+test2
+test3
+

### 2024-02-15 scripts/simulate_data/simulate_data_energy.R
Wrote tests for simulations for fig1 and 2

@@ -7,6 +7,7 @@
 #### Workspace setup ####
 library(tidyverse)
 
+
 #### Simulate data ####
 set.seed(123) # For reproducibility 
 
@@ -16,7 +17,7 @@ years_price <- rep(NA, times=n)
 years_consumption <- rep(NA, times=n)
 
 # Percent of energy price from 2005 to 2007
-# Should be 0.9-1%
+# Should be 0.9-1% for all years
 for (i in 1:3) {
   years_price[i] <- (sample(9:10, 1))/10
 }
@@ -26,7 +27,7 @@ for (i in 1:3) {
 years_price[4] <-(sample(100:105, 1))/100
 
 # Percent of energy price from 2009 to 2010
-# Should be 0.9-1%
+# Should be 0.9-1% for both years
 for (i in 5:6) {
   years_price[i] <- (sample(9:10, 1))/10
 }
@@ -76,4 +77,53 @@ ggplot(simulated_data, aes(x=year)) +
   labs(title = "Relative Energy Price and Consumption", 
        x = "Year", y = "Relative Price/Consumption")
 
+
 #### Test data ####
+
+# Checking that there are only 11 years involved from 2005 to 2015
+simulated_data$year |> length() == 11
+  
+# Checking that the only years involved are from 2005 to 2015 in that order
+simulated_data$year == c(2005, 2006, 2007, 2008, 2009, 2010, 2011, 2012, 2013, 
+                           2014, 2015)
+
+# Checking the classes of the columns
+simulated_data$year |> class() == "integer"
+simulated_data$price |> class() == "numeric"
+simulated_data$consumption |> class() == "numeric"
+
+# Checking that the percent of energy price for all years is between 
+# 0.9% and 1.2%
+between(simulated_data$price, 0.9, 1.2)
+
+# Checking that the percent of energy consumption for all years is between 
+# 0% and 1.1%
+between(simulated_data$consumption, 0, 1.1)
+
+# Checking that the percent of energy price from 2005 to 2007 is between 0.9% 
+# and 1%
+between(simulated_data$price[1:3], 0.9, 1)
+
+# Checking that the percent of energy price in 2008 is between 1% 
+# and 1.05%
+between(simulated_data$price[4], 1, 1.05)
+
+# Checking that the percent of energy price from 2009 to 2010 is between 0.9% 
+# and 1%
+between(simulated_data$price[5:6], 0.9, 1)
+
[…]

### 2024-02-15 scripts/simulate_data/simulate_data_nuclear.R

@@ -7,6 +7,7 @@
 #### Workspace setup ####
 library(tidyverse)
 
+
 #### Simulate data ####
 set.seed(123) # For reproducibility 
 
@@ -21,7 +22,7 @@ for (i in 1:6) {
 }
 
 # Percent of nuclear energy production in 2011
-# Should be 5-10% for all years
+# Should be 5-10%
 years_nuclear[7] <- (sample(5:10, 1))
 
 # Percent of nuclear energy production from 2012 to 2015
@@ -41,3 +42,33 @@ ggplot(simulated_data, aes(x = year, y = percent_nuclear)) +
   geom_point() +
   labs(title = "Percent of Nuclear Energy Produced Domestically", 
        x = "Year", y = "Percent of Nuclear Energy Produced")
+
+
+#### Test data ####
+
+# Checking that there are only 11 years involved from 2005 to 2015
+simulated_data$year |> length() == 11
+
+# Checking that the only years involved are from 2005 to 2015 in that order
+simulated_data$year == c(2005, 2006, 2007, 2008, 2009, 2010, 2011, 2012, 2013, 
+                         2014, 2015)
+
+# Checking the classes of the columns
+simulated_data$year |> class() == "integer"
+simulated_data$percent_nuclear |> class() == "integer"
+
+# Checking that the percent of nuclear energy production for all years is
+# between 0% and 30%
+between(simulated_data$percent_nuclear, 0, 30)
+
+# Checking that the percent of nuclear energy production from 2005 to 2010
+# is between 20% and 30%
+between(simulated_data$percent_nuclear[1:6], 20, 30)
+
+# Checking that the percent of nuclear energy production in 2011 is between
+# 5% and 10%
+between(simulated_data$percent_nuclear[7], 5, 10)
+
+# Checking that the percent of nuclear energy production from 2012 to 2015
+# is between 0% and 5%
+between(simulated_data$percent_nuclear[8:11], 0, 5)

### 2024-02-15 other/ssrp/ssrp_report.qmd
Started ssrp files

---
title: "SSRP Report based on *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019)"
author:
  - Yi Fei Pang
  - Irene Hyunh
  - Tara Chakkithara
thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

# Report

### 2024-02-15 paper/paper.qmd
Added estimand to intro
Started ssrp files

@@
   - Tara Chakkithara
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git SSRP replication available at:"
 date: today
@@
 In this paper, we follow He and Tanaka’s paper (2019) to produce a reproduction of their findings and discuss further about Japan’s future as their government reverses their stance on nuclear energy and begins restarting the use of old power plants as a response to fossil fuel shortages and the public pressure to reduce the country’s carbon footprint.
+The estimand for our study is the effect of energy price on energy consumption.
 We analyze the major reduction in energy consumption from 2005 to 2015 caused by the decline in nuclear energy usage, the sharp increase in electricity prices, and the energy saving campaign pushed by the Japanese government in order to investigate their impact on the mortality rate related to high temperatures.

### 2024-02-15 paper/paper.qmd
Edited footnotes

@@
   - Tara Chakkithara
-thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git SSRP replication available at:"
+thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git"
 date: today

### 2024-02-15 other/ssrp/ssrp_report.qmd
Minor edit tod authors

@@
   - Yi Fei Pang
-  - Irene Hyunh
+  - Irene Huynh
   - Tara Chakkithara

### 2024-02-15 scripts/data_cleaning/clean_nuclear.R
Added preambles to all scripts

@@ -1,3 +1,8 @@
+#### Preamble ####
+# Purpose: Cleans nuclear energy production data in Japan.
+# Date: 14 February 2024
+# License: MIT
+
 library(tidyverse)
 library(readxl)
 library(haven)

### 2024-02-15 scripts/data_cleaning/clean_population.R

@@ -1,3 +1,8 @@
+#### Preamble ####
+# Purpose: Cleans population data in Japan.
+# Date: 14 February 2024
+# License: MIT
+
 library(tidyverse)
 
 data <- read.table("data/raw_data/population.txt", header = TRUE, skip = 2)

### 2024-02-15 scripts/data_cleaning/clean_stroke.R

@@ -1,3 +1,8 @@
+#### Preamble ####
+# Purpose: Cleans heat stroke data in Japan.
+# Date: 14 February 2024
+# License: MIT
+
 library(tidyverse)
 library(haven)
 library(readxl)

### 2024-02-15 scripts/data_cleaning/energy_consumption.R

@@ -1,3 +1,7 @@
+#### Preamble ####
+# Purpose: Cleans energy consumption data in Japan.
+# Date: 14 February 2024
+# License: MIT
 
 library(tidyverse)
 

### 2024-02-15 scripts/data_cleaning/mortality_rate.R

@@ -1,3 +1,8 @@
+#### Preamble ####
+# Purpose: Cleans mortality rate data in Japan.
+# Date: 14 February 2024
+# License: MIT
+
 library(tidyverse)
 
 data <- read_csv("data/analysis_data/population.csv")

### 2024-02-15 scripts/generate_figures/generate_figure1.R

@@ -1,3 +1,8 @@
+#### Preamble ####
+# Purpose: Generates Figure 1.
+# Date: 14 February 2024
+# License: MIT
+
 library(tidyverse)
 library(ggthemes)
 

### 2024-02-15 scripts/generate_figures/generate_figure3.R

@@ -1,3 +1,8 @@
+#### Preamble ####
+# Purpose: Generates Figure 3.
+# Date: 14 February 2024
+# License: MIT
+
 library(tidyverse)
 library(ggthemes)
 

### 2024-02-15 scripts/generate_figures/generate_figure4.R

@@ -1,3 +1,8 @@
+#### Preamble ####
+# Purpose: Generates Figure 4.
+# Date: 14 February 2024
+# License: MIT
+
 library(tidyverse)
 library(ggthemes)
 

### 2024-02-15 scripts/generate_figures/generate_figure5.R

@@ -1,3 +1,8 @@
+#### Preamble ####
+# Purpose: Generates Figure 5.
+# Date: 14 February 2024
+# License: MIT
+
 library(tidyverse)
 library(ggthemes)
 

### 2024-02-15 paper/paper.qmd
added a data + measurement section

@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+In an attempt to understand impact of the Fukushima disaster through data we looked at the changes over time of many variables.
+The first variable we examined was the number of ambulance calls for heatstroke.
+This data was collected from the Fire and Disaster Management Agency in Japan and was a good fit for our analysis as we wanted to really wanted to study the changes in heatstroke occurrences over time.
 
-Talk more about it.
+Additionally, we also considered health datasets which may have helped us analyze heatstroke occurrences directly, but they were all in Japanese and usually consisted of multiple other illnesses making these datasets difficult to parse through.
+We felt that this particular dataset could capture the relationship between heatstroke and time well.
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+Looking at ambulance calls was our way of measuring heatstroke occurrences.
+This way of measurement has the advantage of being concrete while trying to measure health symptoms can be challenging and subjective.
+A flaw with this way of measurement is that it misses people with heatstroke who didn’t call an ambulance.
 
-Talk way more about it.
+The second variable we examined was the domestic energy production of Japan in terajoules.
+We collected this dataset from the International Energy Agency.
+This variable is easy to measure due to the high barrier of entry energy production at a large scale requires.
+Japan has 10 major energy companies that supply energy to the nation and any additional energy production wouldn’t go unnoticed.
+
+Another variable we also considered was Japan’s mortality rate.
+We used the data from the National Institute of Population and Social Security Research of Japan in our analysis due to the reputability of the source.
+Mortality can be difficult to measure considering just how large human populations can be.
+Documenting all cases of mortality may not be possible, especially for people with few friends and family.
+
+Lastly we studied energy consumption (MWH), and the price of 1MWH in yen.
+To study these variables we used data from the Federation of Electric Power Companies of Japan (FEPC).
+This is data directly from the source of Japan’s domestic energy, so we preferred it over other datasets.
+Measuring energy consumption is easy because it has a price tag attached to it.
+Since most transactions occur via the internet these days, it’s pretty easy to keep track of all price and consumption data.
+However, a human error of records could affect the measurements.
 

### 2024-02-15 paper/paper.qmd
added to descriptions of graph 3-5

@@
 ![Figure 1](../other/figures/figure1.png)
-![Figure 5](../other/figures/figure5.png)
+![Figure 3](../other/figures/figure3.png)
+![Figure 4](../other/figures/figure4.png)
 After the Fukushima incident, the government tried to ensure sufficient backup capacity to avoid power blackouts.
 While other factors could affect the saving target, the primary determinant of the saving target was a region’s dependence on nuclear power before the accident.(Kim, et al.) This caused more health issues for individuals as they were encouraged to not use AC and other cooling devices during hotter days.
-Previous to the implementation of the energy policy, throughout the period between 1960 and 2004, the mortality rate at over 32.2 degrees Celsius has dropped tremendously while that of between 26.7-32.3 degrees Celsius remained consistent.
-However, it becomes evident that after the policy implementation, at similar ranges of 25-30 degrees Celsius and over 30 degrees Celsius produced a higher mortality rate.
-[figure 5]
+Previous to the implementation of the energy policy, throughout the period between 1960 and 2004, the mortality rate was significantly lower (closer to 0.87) while the mortality rate after was much higher (close to 0.95)[figure 3].
+In addition, the mortality rate for heatstrokes also increased dramatically in the year 2011 more than doubling that of 2010.
+Moreover, the mortality risk caused by electricity saving is particularly high in the summer, during which the energy-saving campaigns are intensively promoted.
+To account for the potential “harvesting effect” or “delayed effect,” we also estimate distributed lag models on the impacts of temperature and the energy-saving policy.
+Taking into account this dynamic impact, it is estimated that the energy-saving campaigns could have led to nearly 7,710 premature deaths annually in Japan (Kim, et al.).
+Lastly, there is a trend where the higher the saving targets, the higher the increase in the mortality rate during the hot days (between 25–30°C and above 30°C), but a relatively moderate increase for cold temperatures (below 0°C and 0–5°C) (Kim et.
+al).
 
@@
 As aforementioned, the datasets only extend until 2016 and to complete a long-term analysis, more recent Japanese energy data needs to be collected.
-Moreover, data from before and after other global nuclear incidents should be gathered and evalauted in comparison to Fukushima to evaluate whether the Japanese government's apporoach was the most optimal.
-Another step that can be taken to futher the analysis could be to explore more granular effects.
+Moreover, data from before and after other global nuclear incidents should be gathered and evaluated in comparison to Fukushima to evaluate whether the Japanese government's approach was the most optimal.
+Another step that can be taken to further the analysis could be to explore more granular effects.
 For example, in addition to looking at how ambulance calls and heat strokes can be correlated and how increased temperature can cause higher mortality rates before and after the energy policy, other factors such as energy price variation and seasons or energy jobs and employment rates can be observed as well.

### 2024-02-15 other/ssrp/ssrp_report.qmd
first draft

@@
 author:
+  - Tara Chakkithara
+  - Irene Huynh
   - Yi Fei Pang
-  - Irene Huynh
-  - Tara Chakkithara
+
 thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git"
@@
 date-format: long
-format: pdf
+format: 
+  pdf: 
+    documentclass: article
 number-sections: true
@@
 
-# Report
+During our analysis, we reproduced three figures of interest from "Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident" by He and Tanaka (2019).
+As highlighted in our data section, we were particularly interested in the variables domestic energy consumption, price, nuclear production.
+Thus we chose to reproduce the figures 1A, 1B, and G1.
+
+All reproductions were done using R and tidyverse.
+
+Reproduction 1 : Figure1A
+![Domestic Nuclear Energy Production](../figures/figure1.png)
+
+Reproduction 2 : Figure1B
+![Electricity Consumption and Price Relative to 2011](../figures/figure2.png)

### 2024-02-15 scripts/generate_figures/generate_figure1.R

@@ -1,46 +1,22 @@
 #### Preamble ####
-# Purpose: Generates Figure 1.
+# Purpose: Generates Figure 2.
 # Date: 14 February 2024
 # License: MIT
 
 library(tidyverse)
 library(ggthemes)
 
-data <- read_csv("data/analysis_data/consumption.csv")
-data
-
-data <- data |>
-  select(year, total_energy, price) |>
-  group_by(year) |>
-  summarise(total_energy = mean(total_energy), price = mean(price))
-mean_price_2011 <- 16.92426	
-mean_consumption_2011 <- 7163859
-
-data <- data |>
-  mutate(
-    relative_consumption = total_energy/mean_consumption_2011,
-    relative_price = price/mean_price_2011
-  )
-data |>
-  select(year, relative_consumption, relative_price)
+data <- read_csv("data/analysis_data/clean_domestic.csv")
 
 plot <- data |>
   ggplot(
-    mapping = aes(x = year)
+    aes(x = year)
   ) +
   theme_fivethirtyeight() +
-  theme(
-    plot.background = element_rect(fill = "white"),
-    panel.grid = element_line(color = "black"),
-    panel.background = element_rect(fill = "white")
-  ) +
+  theme_bw() +
   scale_x_continuous(breaks = data$year) +
-  geom_point(aes(y = relative_consumption, color = "Energy Consumption")) +
-  geom_path(aes(y = relative_consumption), linetype = "dotted") +
-  geom_point(aes(y = relative_price, color = "Price")) +
-  geom_path(aes(y = relative_price), linetype="dotdash") +
-  geom_hline(yintercept = 1) +
-  ggtitle("Relative Energy Consumption and Price") +
-  labs(caption = "FIGURE 1", color = "")
+  geom_point(aes(y = percent_nuclear)) +
+  geom_path(aes(y = percent_nuclear)) +
+  labs(x = "Year")
 
 ggsave("other/figures/figure1.png", plot)

### 2024-02-15 scripts/generate_figures/generate_figure2.R

@@ -1,22 +1,45 @@
 #### Preamble ####
-# Purpose: Generates Figure 2.
+# Purpose: Generates Figure 1.
 # Date: 14 February 2024
 # License: MIT
 
 library(tidyverse)
+library(ggthemes)
 
-data <- read_csv("data/analysis_data/clean_domestic.csv")
+data <- read_csv("data/analysis_data/consumption.csv")
+data
+
+data <- data |>
+  select(year, total_energy, price) |>
+  group_by(year) |>
+  summarise(total_energy = mean(total_energy), price = mean(price))
+mean_price_2011 <- 16.92426	
+mean_consumption_2011 <- 7163859
+
+data <- data |>
+  mutate(
+    relative_consumption = total_energy/mean_consumption_2011,
+    relative_price = price/mean_price_2011
+  )
+data |>
+  select(year, relative_consumption, relative_price)
 
 plot <- data |>
   ggplot(
-    aes(x = year)
+    mapping = aes(x = year)
   ) +
   theme_fivethirtyeight() +
-  theme_bw() +
+  theme(
+    plot.background = element_rect(fill = "white"),
+    panel.grid = element_line(color = "black"),
+    panel.background = element_rect(fill = "white")
+  ) +
   scale_x_continuous(breaks = data$year) +
-  geom_point(aes(y = percent_nuclear)) +
-  geom_path(aes(y = percent_nuclear)) +
-  labs(x = "Year", y = "Percent of Nuclear Energy Produced") +
-  ggtitle("Percent of Nuclear Energy Produced Domestically")
+  geom_point(aes(y = relative_consumption, color = "Energy Consumption")) +
+  geom_path(aes(y = relative_consumption), linetype = "dotted") +
+  geom_point(aes(y = relative_price, color = "Price")) +
+  geom_path(aes(y = relative_price), linetype="dotdash") +
+  geom_hline(yintercept = 1) +
+  labs(caption = "FIGURE 1", color = "")
 
 ggsave("other/figures/figure2.png", plot)

### 2024-02-15 scripts/generate_figures/generate_figure3.R

@@ -12,13 +12,17 @@ data <- data |>
   group_by(year >= 2010) |>
   summarise(avg_rate = mean(dr)*100) |>
   ungroup() |>
-  rename(policy = "year >= 2010")
+  rename(policy = "year >= 2010") |>
+  mutate(policy = case_when(
+    policy == TRUE ~ "Post-Policy",
+    policy == FALSE ~ "Initial")
+  )
 
 plot <- data |>
   ggplot(aes(x = policy)) +
   theme_fivethirtyeight() +
   theme_bw() +
   geom_point(aes(y = avg_rate)) +
-  labs(x = "Policy", y = "Mortality Rate (%)")
+  labs(y = "Mortality", x = "")
 
 ggsave("other/figures/figure3.png", plot)

### 2024-02-15 paper/paper.qmd
added Summary Data and added results analysis of summary data

@@
 # Results
-
-Our results are summarized in @tbl-modelresults.
+Based on the temperature summary data, it's observed that Summers can get quite hot with highs of over 32 degrees Celsius.
+That alongside rising electricity prices over the analysed period (mean > median) and an implementation of an energy conservation target.
+It's easy to deduce the likely hood of an extreme increase in heatstrokes with the mean people transported sitting at almost four times the median.
+When observing data between temperature and energy usage, there should be a correlation between extreme weather and energy use.
+As cold weather would prompt higher usage of heaters while hot weather would prompt higher usage of AC.
+Post Fukushima, the energy usage did not keep up with the extreme weather which took a toll on different aspects such as higher number of heatstroke victims and increased mortality rate.
+Furthermore, with respect to energy consumption data, there is an extremely high third quantile of almost 6.5 million MWH which suggests higher ranges of energy consumption.
+This can be indicative of overuse of energy resources, perhaps stemming from an abrupt switch from nuclear energy to fossil fuels.
+Finally, all of this is reflective in the massive energy price fluctuations of around 13 yen per MWH to over 23 yen.
+These fluctuations are indicative of a very unstable energy market which can be the results of the energy source shift and the energy policy.
 

### 2024-02-15 paper/paper.qmd
Formatted figures for the pdf

@@
 
-The remainder of this paper is structured as follows: the Data section details the collection
-and processing of nuclear energy production, energy consumption, energy price, and temperature-mortality data.
+The remainder of this paper is structured as follows: the Data section details the collection and processing of nuclear energy production, energy consumption, energy price, and temperature-mortality data.
 Additionally, the section includes discussion on the measurement of the original dataset.
-The following Results section displays and analyzes tables
-and figures that illustrate the trends found in the data. The Discussion section draws conclusions from those tables and figures and details the importance of our findings and weaknesses of our paper.
+The following Results section displays and analyzes tables and figures that illustrate the trends found in the data.
+The Discussion section draws conclusions from those tables and figures and details the importance of our findings and weaknesses of our paper.
 
-![Figure 1](../other/figures/figure1.png)
-![Figure 3](../other/figures/figure3.png)
-![Figure 4](../other/figures/figure4.png)
+![Relative Energy Consumption and Price](../other/figures/figure1.png){#fig-energy}
+
+![Mortality Rate and Policy](../other/figures/figure3.png){#fig-mortality}
+
+![Number of Heatstroke Incidents from 2008 to 2015](../other/figures/figure4.png){#fig-heatstrokeIncidents}
+
 After the Fukushima incident, the government tried to ensure sufficient backup capacity to avoid power blackouts.
@@
 However, a human error of records could affect the measurements.
-
-# Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-\newpage
-
 # References

### 2024-02-15 scripts/generate_figures/generate_figure1.R

@@ -39,8 +39,6 @@ plot <- data |>
   geom_path(aes(y = relative_consumption), linetype = "dotted") +
   geom_point(aes(y = relative_price, color = "Price")) +
   geom_path(aes(y = relative_price), linetype="dotdash") +
-  geom_hline(yintercept = 1) +
-  ggtitle("Relative Energy Consumption and Price") +
-  labs(caption = "FIGURE 1", color = "")
+  geom_hline(yintercept = 1)
 
 ggsave("other/figures/figure1.png", plot)

### 2024-02-15 paper/paper.qmd
Reverted some changes from previous commit

@@
 
-![Relative Energy Consumption and Price](../other/figures/figure1.png){#fig-energy}
-
-![Mortality Rate and Policy](../other/figures/figure3.png){#fig-mortality}
-
-![Number of Heatstroke Incidents from 2008 to 2015](../other/figures/figure4.png){#fig-heatstrokeIncidents}
+![Figure 1](../other/figures/figure1.png)
+![Figure 3](../other/figures/figure3.png)
+![Figure 4](../other/figures/figure4.png)
 

### 2024-02-15 scripts/generate_figures/generate_figure1.R

@@ -39,6 +39,8 @@ plot <- data |>
   geom_path(aes(y = relative_consumption), linetype = "dotted") +
   geom_point(aes(y = relative_price, color = "Price")) +
   geom_path(aes(y = relative_price), linetype="dotdash") +
-  geom_hline(yintercept = 1)
+  geom_hline(yintercept = 1)  +
+  ggtitle("Relative Energy Consumption and Price") +
+  labs(caption = "FIGURE 1", color = "")
 
 ggsave("other/figures/figure1.png", plot)

### 2024-02-15 scripts/generate_figures/generate_figure1.R
fixed figures

@@ -1,46 +1,22 @@
 #### Preamble ####
-# Purpose: Generates Figure 1.
+# Purpose: Generates Figure 2.
 # Date: 14 February 2024
 # License: MIT
 
 library(tidyverse)
-library(ggthemes)
 
-data <- read_csv("data/analysis_data/consumption.csv")
-data
-
-data <- data |>
-  select(year, total_energy, price) |>
-  group_by(year) |>
-  summarise(total_energy = mean(total_energy), price = mean(price))
-mean_price_2011 <- 16.92426	
-mean_consumption_2011 <- 7163859
-
-data <- data |>
-  mutate(
-    relative_consumption = total_energy/mean_consumption_2011,
-    relative_price = price/mean_price_2011
-  )
-data |>
-  select(year, relative_consumption, relative_price)
+data <- read_csv("data/analysis_data/clean_domestic.csv")
 
 plot <- data |>
   ggplot(
-    mapping = aes(x = year)
+    aes(x = year)
   ) +
   theme_fivethirtyeight() +
-  theme(
-    plot.background = element_rect(fill = "white"),
-    panel.grid = element_line(color = "black"),
-    panel.background = element_rect(fill = "white")
-  ) +
+  theme_bw() +
   scale_x_continuous(breaks = data$year) +
-  geom_point(aes(y = relative_consumption, color = "Energy Consumption")) +
-  geom_path(aes(y = relative_consumption), linetype = "dotted") +
-  geom_point(aes(y = relative_price, color = "Price")) +
-  geom_path(aes(y = relative_price), linetype="dotdash") +
-  geom_hline(yintercept = 1)  +
-  ggtitle("Relative Energy Consumption and Price") +
-  labs(caption = "FIGURE 1", color = "")
+  geom_point(aes(y = percent_nuclear)) +
+  geom_path(aes(y = percent_nuclear)) +
+  labs(x = "Year", y = "Percent of Nuclear Energy") +
+  ggtitle("Domestic Energy Production")
 
 ggsave("other/figures/figure1.png", plot)

### 2024-02-15 scripts/generate_figures/generate_figure2.R

@@ -1,22 +1,46 @@
 #### Preamble ####
-# Purpose: Generates Figure 2.
+# Purpose: Generates Figure 1.
 # Date: 14 February 2024
 # License: MIT
 
 library(tidyverse)
+library(ggthemes)
 
-data <- read_csv("data/analysis_data/clean_domestic.csv")
+data <- read_csv("data/analysis_data/consumption.csv")
+data
+
+data <- data |>
+  select(year, total_energy, price) |>
+  group_by(year) |>
+  summarise(total_energy = mean(total_energy), price = mean(price))
+mean_price_2011 <- 16.92426	
+mean_consumption_2011 <- 7163859
+
+data <- data |>
+  mutate(
+    relative_consumption = total_energy/mean_consumption_2011,
+    relative_price = price/mean_price_2011
+  )
+data |>
+  select(year, relative_consumption, relative_price)
 
 plot <- data |>
   ggplot(
-    aes(x = year)
+    mapping = aes(x = year)
   ) +
   theme_fivethirtyeight() +
-  theme_bw() +
+  theme(
+    plot.background = element_rect(fill = "white"),
+    panel.grid = element_line(color = "black"),
+    panel.background = element_rect(fill = "white")
+  ) +
   scale_x_continuous(breaks = data$year) +
-  geom_point(aes(y = percent_nuclear)) +
-  geom_path(aes(y = percent_nuclear)) +
-  labs(x = "Year", y = "Percent of Nuclear Energy Produced") +
-  ggtitle("Percent of Nuclear Energy Produced Domestically")
+  geom_point(aes(y = relative_consumption, color = "Electricity Consumption")) +
+  geom_path(aes(y = relative_consumption), linetype = "dotted") +
+  geom_point(aes(y = relative_price, color = "Price")) +
+  geom_path(aes(y = relative_price), linetype="dotdash") +
+  geom_hline(yintercept = 1)  +
+  ggtitle("Relative Electricity Consumption and Price") +
+  labs(caption = "FIGURE 2", color = "")
 
 ggsave("other/figures/figure2.png", plot)

### 2024-02-15 scripts/generate_figures/generate_figure3.R

@@ -12,7 +12,13 @@ data <- data |>
   group_by(year >= 2010) |>
   summarise(avg_rate = mean(dr)*100) |>
   ungroup() |>
-  rename(policy = "year >= 2010")
+  rename(policy = "year >= 2010") |>
+  mutate(
+    policy = case_when(
+      policy == FALSE ~ "Before Policy",
+      policy == TRUE ~ "Post Policy"
+    )
+  )
 
 plot <- data |>
   ggplot(aes(x = policy)) +

### 2024-02-15 data/raw_data/weather/csv/get.py
del not needed

@@ -1,9 +1,0 @@
-# import requests
-# url_city= "https://www.data.jma.go.jp/gmd/risk/obsdl/top/station"
-# payload = {   
-#     'pd': '11'
-# }
-# citylist = requests.post(url_city,data = payload)
-# print(citylist.text)
-
-import pandas as pd

### 2024-02-15 paper/paper.qmd
Added figure captions

@@
 ![Figure 1](../other/figures/figure1.png)
+![Figure 2](../other/figures/figure2.png)
 ![Figure 3](../other/figures/figure3.png)
 ![Figure 4](../other/figures/figure4.png)
+![Figure 5](../other/figures/figure5.png)
 

### 2024-02-15 scripts/generate_figures/generate_figure1.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Generates Figure 2.
+# Purpose: Generates Figure 1.
 # Date: 14 February 2024
 # License: MIT
 
@@ -17,6 +17,7 @@ plot <- data |>
   geom_point(aes(y = percent_nuclear)) +
   geom_path(aes(y = percent_nuclear)) +
   labs(x = "Year", y = "Percent of Nuclear Energy") +
-  ggtitle("Domestic Energy Production")
+  labs(caption = "FIGURE 1: Domestic Nuclear Energy Production", color = "") +
+  theme(plot.caption=element_text(hjust=0.5))
 
 ggsave("other/figures/figure1.png", plot)

### 2024-02-15 scripts/generate_figures/generate_figure2.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Generates Figure 1.
+# Purpose: Generates Figure 2.
 # Date: 14 February 2024
 # License: MIT
 
@@ -39,8 +39,8 @@ plot <- data |>
   geom_path(aes(y = relative_consumption), linetype = "dotted") +
   geom_point(aes(y = relative_price, color = "Price")) +
   geom_path(aes(y = relative_price), linetype="dotdash") +
-  geom_hline(yintercept = 1)  +
-  ggtitle("Relative Electricity Consumption and Price") +
-  labs(caption = "FIGURE 2", color = "")
+  geom_hline(yintercept = 1)+
+  labs(caption = "FIGURE 2: Relative Electricity Consumption and Price", color = "") +
+  theme(plot.caption=element_text(hjust=0.5))
 
 ggsave("other/figures/figure2.png", plot)

### 2024-02-15 scripts/generate_figures/generate_figure3.R

@@ -25,6 +25,8 @@ plot <- data |>
   theme_fivethirtyeight() +
   theme_bw() +
   geom_point(aes(y = avg_rate)) +
-  labs(x = "Policy", y = "Mortality Rate (%)")
+  labs(x = "Policy", y = "Mortality Rate (%)") +
+  labs(caption = "FIGURE 3: Mortality Rate and Energy Policy", color = "")  +
+  theme(plot.caption=element_text(hjust=0.5))
 
 ggsave("other/figures/figure3.png", plot)

### 2024-02-15 scripts/generate_figures/generate_figure4.R

@@ -18,6 +18,8 @@ plot <- data |>
   ) +
   geom_bar(stat = "identity", fill = "lavender") +
   theme_test() +
-  labs(x = "Period", y = "Number of Heatstroke Incidents")
+  labs(x = "Period", y = "Number of Heatstroke Incidents") +
+  labs(caption = "FIGURE 4: Heatstroke Incidents from 2008 to 2015", color = "") +
+  theme(plot.caption=element_text(hjust=0.5))
 
 ggsave("other/figures/figure4.png", plot)

### 2024-02-15 scripts/generate_figures/generate_figure5.R

@@ -27,7 +27,9 @@ plot <- data |>
   geom_line(key_glyph = "point") +
   theme_bw() +
   theme(panel.background = element_rect(fill = "white")) +
-  labs(x = "Period", y = "Heatstroke Incidents", color = "Prefecture")
+  labs(x = "Period", y = "Heatstroke Incidents", color = "Prefecture") +
+  labs(caption = "FIGURE 5: Heatstroke Incidents from 2008 to 2015 in Each Prefecture")  +
+  theme(plot.caption=element_text(hjust=0.5))
 
 
 ggsave("other/figures/figure5.png", plot)

### 2024-02-15 other/ssrp/ssrp_report.qmd
Wrote ssrp

--- 2024-02-15 other/ssrp/ssrp_report.qmd
@@
 # Report
+
+The statistical programming language R was used to acquire, clean, and process the data [@citeR].
+In particular, the following R packages were used: tidyverse [@tidyverse], readxl [@readxl], haven [@haven], ggthemes [@ggthemes], and ggplot2 [@ggplot2].
+
+Three figures from *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019) were reproduced:
+
+- Figure 1 is a reproduction of Figure 1A. from He and Tanaka (2019).
+- Figure 2 is a reproduction of Figure 1B. from He and Tanaka (2019).
+- Figure 3 is a reproduction of Figure G1. from He and Tanaka (2019).
+
+![](../../other/figures/figure1.png)
+
+![](../../other/figures/figure2.png)
+![](../../other/figures/figure3.png)
+\newpage
+
+# References

### 2024-02-15 other/ssrp/ssrp_report.qmd
Modified ssrp

@@
 format: pdf
-number-sections: true
 bibliography: references.bib

### 2024-02-15 other/ssrp/ssrp_report.qmd
Added to ssrp

@@
 
-The statistical programming language R was used to acquire, clean, and process the data [@citeR].
+To reproduce figures from *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019), the statistical programming language R was used to acquire, clean, and process the data [@citeR].
 In particular, the following R packages were used: tidyverse [@tidyverse], readxl [@readxl], haven [@haven], ggthemes [@ggthemes], and ggplot2 [@ggplot2].

### 2024-02-15 paper/paper.qmd
Cleaned up sections and editted intro

--- 2024-02-15 paper/paper.qmd
@@
 
+The government's energy-saving policies included energy-saving targets to be met.
+While many factors could affect the saving target, the primary determinant of the saving target was a region’s dependence on nuclear power before the accident (Kim, et al.) This caused more health issues for individuals as they were encouraged to not use air conditioning and other cooling devices during hotter days.
+Prior to the implementation of the energy policy, throughout the period between 1960 and 2004, the mortality rate during high temperatures was significantly lower (closer to 0.87) while the mortality rate after was much higher (close to 0.95) [see Figure 3].
+In addition, the mortality rate for heat strokes increased dramatically in the year 2011 more than doubling that of 2010.
+Moreover, the mortality risk caused by electricity saving is particularly high in the summer, during which the energy-saving campaigns are intensively promoted.
+To account for the potential “harvesting effect” or “delayed effect,” we also estimate distributed lag models on the impacts of temperature and the energy-saving policy.
+Taking into account this dynamic impact, it is estimated that the energy-saving campaigns could have led to nearly 7,710 premature deaths annually in Japan (Kim, et al.).
+Furthermore, there is a trend where the higher the saving targets, the higher the increase in the mortality rate during the hot days (between 25–30°C and above 30°C), but a relatively moderate increase for cold temperatures (below 0°C and 0–5°C) (Kim et.
+al).
+
 In this paper, we follow He and Tanaka’s paper (2019) to produce a reproduction of their findings and discuss further about Japan’s future as their government reverses their stance on nuclear energy and begins restarting the use of old power plants as a response to fossil fuel shortages and the public pressure to reduce the country’s carbon footprint.
@@
 
-![Figure 1](../other/figures/figure1.png)
-![Figure 3](../other/figures/figure3.png)
-![Figure 4](../other/figures/figure4.png)
+# Data {#sec-data}
 
-After the Fukushima incident, the government tried to ensure sufficient backup capacity to avoid power blackouts.
-While other factors could affect the saving target, the primary determinant of the saving target was a region’s dependence on nuclear power before the accident.(Kim, et al.) This caused more health issues for individuals as they were encouraged to not use AC and other cooling devices during hotter days.
-Previous to the implementation of the energy policy, throughout the period between 1960 and 2004, the mortality rate was significantly lower (closer to 0.87) while the mortality rate after was much higher (close to 0.95)[figure 3].
-In addition, the mortality rate for heatstrokes also increased dramatically in the year 2011 more than doubling that of 2010.
-Moreover, the mortality risk caused by electricity saving is particularly high in the summer, during which the energy-saving campaigns are intensively promoted.
-To account for the potential “harvesting effect” or “delayed effect,” we also estimate distributed lag models on the impacts of temperature and the energy-saving policy.
-Taking into account this dynamic impact, it is estimated that the energy-saving campaigns could have led to nearly 7,710 premature deaths annually in Japan (Kim, et al.).
-Lastly, there is a trend where the higher the saving targets, the higher the increase in the mortality rate during the hot days (between 25–30°C and above 30°C), but a relatively moderate increase for cold temperatures (below 0°C and 0–5°C) (Kim et.
-al).
+## Sources
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
+To create our figures and reproduce figures from *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019), the statistical programming language R was used to acquire, clean, and process the data [@citeR].
+In particular, the following R packages were used: tidyverse [@tidyverse], readxl [@readxl], haven [@haven], ggthemes [@ggthemes], and ggplot2 [@ggplot2].
 
-The remainder of this paper is structured as follows. @sec-data....
-
-# Data {#sec-data}
+## Variables and Measurement
 
@@
 
+\newpage
 # Results
+![](../other/figures/figure1.png)
+\newpage
+![](../other/figures/figure2.png)
+\newpage
+![](../other/figures/figure3.png)
+\newpage
+![](../other/figures/figure4.png)
+\newpage
+![](../other/figures/figure5.png)
+
 Based on the temperature summary data, it's observed that Summers can get quite hot with highs of over 32 degrees Celsius.
